---
title: "470th Gdelt Data Analysis"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: yes
    number_sections: yes
    includes:
      in_header: header.tex
---

```{r setup, include=FALSE}
  library(ggplot2)
  library(knitr)
  library(dplyr)
  library(mapproj)
  library(scales)
  library(RgoogleMaps)
# The following code formats the gdelt .csv file into a more readable format using variables defined in the 
# Gdelt 2.0 codebook. 
# date <- Sys.Date()
# date <- gsub("-","", date)
# #url <- paste("http://data.gdeltproject.org/events/", ".export.CSV.zip", sep = date)
# url <- "http://data.gdeltproject.org/events/20170718.export.CSV.zip"
# 
#     # download .zip file and unzip contents
#     download.file(url, dest="dataset.zip", mode="wb") 
#     unzip ("dataset.zip", exdir = "./")
#     unlink("dataset.zip")
# #csv <- paste(date, ".export.CSV", sep="")
info2 <- read.csv("20170727181500.export.CSV",sep = "\t",header = TRUE, as.is = TRUE, na.strings = "NA", col.names = c("GlobalEventID","Day","MonthYear","Year","FractionDate","Actor1Code",
                                                                                "Actor1Name","Actor1CountryCode","Actor1KnownGroupCode","Actor1EthnicCode","Actor1Religion1Code","Actor1Religion2Code","Actor1Type1Code","Actor1Type2Code",
                                                                                      "Actor1Type3Code","Actor2Code","Actor2Name","Actor2CountryCode","Actor2KnownGroupCode","Actor2EthnicCode", "Actor2Religion1Code","Actor2Religion2Code","Actor2Type1Code",
                                                                                      "Actor2Type2Code","Actor2Type3Code","IsRootEvent","EventCode","EventBaseCode","EventRootCode","QuadClass","GoldsteinScale",
                                                                                      "NumMentions","NumSources","NumArticles","AvgTone","Actor1Geo_Type","Actor1Geo_Fullname","Actor1Geo_CountryCode","Actor1Geo_ADM1Code","Actor1Geo_ADM2Code","Actor1Geo_Lat","Actor1Geo_Long","Actor1Geo_FeatureID","Actor2Geo_Type","Actor2Geo_Fullname","Actor2Geo_CountryCode",
                                                                                      "Actor2Geo_AMD1Code","Actor2Geo_AMD2Code","Actor2Geo_Lat","Actor2Geo_Long","Actor2Geo_FeatureID","ActionGeo_Type","ActionGeo_Fullname",
                                                                                      "ActionGeo_CountryCode","ActionGeo_AMD1Code","ActionGeo_AMD2Code","ActionGeo_Lat","ActionGeo_Long","ActionGeo_FeatureID","Dateadded","Sourceurl") )



info2$X <- seq.int(nrow(info2))
info2 <- info2[,c("X", setdiff(names(info2), "X"))]


sa2 <- c("GT","SV","GP","PA","PR","GY","CO","EC","PY","SR","UY","VE","PE","SR","GF","FK","CL", "BR", "AR", "CU","CR","BB","BS","AW","AI","HN")
ca2 <- dplyr::filter(info2, ActionGeo_CountryCode %in% sa2)


```

# Quad Class

**QuadClass** : (integer) The entire CAMEO event taxonomy is ultimately organized under four primary classifications: Verbal Cooperation, Material Cooperation, Verbal Conflict, and Material Conflict. This field specifies this primary classification for the event type, allowing analysis at the highest level of aggregation. The numeric codes in this field map to the Quad Classes as follows: 1=Verbal Cooperation, 2=Material Cooperation, 3=Verbal Conflict, 4=Material Conflict.

```{r quadSetup, echo = FALSE}
  quad <- info2
  for(i in 0:nrow(quad)){
    if (4 %in% quad$QuadClass[i]){
      quad$QuadClass[i] <- "4 Material Conflict"
    } else if (3 %in% quad$QuadClass[i]){
      quad$QuadClass[i] <- "3 Verbal Conflict"
    } else if (2 %in% quad$QuadClass[i]){
      quad$QuadClass[i] <- "2 Material Cooperation"
    } else if (1 %in% quad$QuadClass[i]){
      quad$QuadClass[i] <- "1 Verbal Cooperation"
   }
  }

```

## Quad Class Bar Graph

```{r bargraph, echo = FALSE}

  ggplot(data = quad, aes( x = QuadClass)) + geom_bar(fill = "lightblue", color= "darkblue", width = .5) + 
  xlab("Quad Class of the Events") + 
  theme(axis.title.y = element_blank()) + ggtitle("Number of Events by Quad Class")
  
```


## Quad Class Article Tone

```{r articletone, echo = FALSE}
  
  quadTone <- summarise (group_by(quad, QuadClass) , meanTone =   mean(AvgTone))
  ggplot(quadTone, aes(x = QuadClass, y = meanTone)) +  
  geom_bar(stat = "identity", width = .5) +
  xlab("Quad Class of the Events")
  
```

# Event Code

**EventBaseCode**: (string) CAMEO event codes are defined in a three-level taxonomy. For events at level three in the taxonomy, this yields its level two leaf root node. For example, code “0251” (“Appeal for easing of administrative sanctions”) would yield an EventBaseCode of “025” (“Appeal to yield”). This makes it possible to aggregate events at various resolutions of specificity. For events at levels two or one, this field will be set to EventCode. NOTE: it is strongly recommended that this field be stored as a string instead of an integer, since the CAMEO taxonomy can include zero-leaded event codes that can make distinguishing between certain event types more difficult when stored as an integer.

* LEGEND:
* 01	MAKE PUBLIC STATEMENT
* 02	APPEAL
* 03	EXPRESS INTENT TO COOPERATE
* 04	CONSULT
* 05	ENGAGE IN DIPLOMATIC COOPERATION
* 06	ENGAGE IN MATERIAL COOPERATION
* 07	PROVIDE AID
* 08	YIELD
* 09	INVESTIGATE
* 10	DEMAND
* 11	DISAPPROVE
* 12	REJECT
* 13	THREATEN
* 14	PROTEST
* 15	EXHIBIT FORCE POSTURE
* 16	REDUCE RELATIONS
* 17	COERCE
* 18	ASSAULT
* 19	FIGHT
* 20	USE UNCONVENTIONAL MASS VIOLENCE



## Event Code Bar Graph
```{r EventCode, echo = FALSE}
  ca2$EventBaseCode <- as.factor(ca2$EventBaseCode)

  ggplot(ca2, aes(x = EventRootCode)) +
  geom_bar(fill = "blue", colour = "black", width = .5) +
  theme(axis.text.x = element_text(angle = 90, hjust = .5, vjust = .5)) +
  xlab("Event Code") +
  theme(axis.title.y = element_blank())+
  ggtitle("Number of Events by Event Code ")
  
```  


# Country Code

**Country Code**: (string) This is the 2-character FIPS10-4 country code for the location.

## Country Code Bar Graph
```{r ActionGeo_CountryCode, echo = FALSE}
  ca2$ActionGeo_CountryCode <- as.factor(ca2$ActionGeo_CountryCode)

  ggplot(ca2, aes(x = ActionGeo_CountryCode)) +
  geom_bar(fill = "blue", colour = "black", width = .5) +
  theme(axis.text.x = element_text(angle = 90, hjust = .5, vjust = .5)) +
  xlab("Country Code") +
  theme(axis.title.y = element_blank()) +
  ggtitle("Number of Events by Country Code ")
  

```

# Number of Mentions, Total and Per Article

**Number of Mentions**:(integer) This is the total number of mentions of this event across all source documents during the 15 minute update in which it was first seen. Multiple references to an event within a single document also contribute to this count. This can be used as a method of assessing the “importance” of an event: the more discussion of that event, the more likely it is to be significant. The total universe of source documents and the density of events within them vary over time, so it is recommended that this field be normalized by the average or other measure of the universe of events during the time period of interest. This field is actually a composite score of the total number of raw mentions and the number of mentions extracted from reprocessed versions of each article (see the discussion for the Mentions table). NOTE: this field refers only to the first news report to mention an event and is not updated if the event is found in a different context in other news reports.  

## Number of Mentions Bar Graph
```{r NumMentions, echo = FALSE}
  ca2$NumMentions <- as.factor(ca2$NumMentions)

  ggplot(ca2, aes(x = NumMentions)) +
  geom_bar(fill = "blue", colour = "black", width = .5) +
  theme(axis.text.x = element_text(angle = 90, hjust = .5, vjust = .5)) +
  xlab("Number of Mentions") +
  theme(axis.title.y = element_blank()) +
  ggtitle("Number of Mentions")

```

**Number of Articles**: (integer) This is the total number of source documents containing one or more mentions of this event during the 15 minute update in which it was first seen. This can be used as a method of assessing the “importance” of an event: the more discussion of that event, the more likely it is to be significant. The total universe of source documents varies over time, so it is recommended that this field be normalized by the average or other measure of the universe of events during the time period of interest. NOTE: this field refers only to the first news report to mention an event and is not updated if the event is found in a different context in other news reports. 

## Number of Articles Bar Graph
```{r NumArticles, echo = FALSE}
  ca2$NumArticles <- as.factor(ca2$NumArticles)

  ggplot(ca2, aes(x = NumArticles)) +
  geom_bar(fill = "blue", colour = "black", width = .5) +
  theme(axis.text.x = element_text(angle = 90, hjust = .5, vjust = .5)) +
  xlab("Number of Articles") +
  theme(axis.title.y = element_blank()) +
  ggtitle("Number of Articles")

```

# SourceURL

**SourceURL**: (string) This field records the URL or citation of the first news report it found this event in. In most cases this is the first report it saw the article in, but due to the timing and flow of news reports through the processing pipeline, this may not always be the very first report, but is at least in the first few reports.

## SourceURL Bar Graph
```{r Sourceurl, echo = FALSE}
  ca2$Sourceurl <- as.factor(ca2$Sourceurl)
  ca2$Sourceurl <- urltools::domain(ca2$Sourceurl)
  ggplot(ca2, aes(x = Sourceurl)) +
  geom_bar(fill = "blue", colour = "black", width = .5) +
  theme(axis.text.x = element_text(angle = 90, hjust = .5, vjust = .5)) +
  xlab("SourceURL") +
  theme(axis.title.y = element_blank()) +
  ggtitle("SourceURL")


```


